### 2019-02-19 report/final-report.tex
some work on the methods section

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{amsmath}
\usepackage[capitalise]{cleveref}
\usepackage{makecell}%To keep spacing of text in tables
\usepackage{nccmath}
\usepackage{mathtools}
\usepackage{bussproofs}
\usepackage{varwidth}
\usepackage{amsthm}
\usepackage{csvsimple}
\usepackage{thmtools,thm-restate}
\usepackage{changepage}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{multirow,bigdelim}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{letltxmacro}
\usepackage{sansmath}
\usepackage{url}
\usepackage{flushend}
\usepackage{microtype}
\usepackage[utf8]{inputenc}
\usepackage{mathpartir}
\usepackage{empheq}
\usepackage{array}
\usepackage{pgfplots}
\usepackage{stmaryrd}
\usepackage{courier}
\usepackage{qtree}
\usepackage[normalem]{ulem}
\usepackage{relsize}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{tabularx}
\usepackage{stackengine}
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{remreset}
\usepackage{tabulary}
\usepackage{xspace}
\usepackage{bbm}

@@

\section{Summary}

\section{Introduction}

@@

We have written three academic papers~\cite{?}
describing and evaluating our algorithms and produced open-source our code.

\section{Methods, Assumptions, and Procedures}

\section{Results and Discussion}

@@

\section{Conclusions}

>>>>

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{amsmath}
\usepackage[capitalise]{cleveref}
\usepackage{makecell}%To keep spacing of text in tables
\usepackage{nccmath}
\usepackage{mathtools}
\usepackage{bussproofs}
\usepackage{varwidth}
\usepackage{amsthm}
\usepackage{csvsimple}
\usepackage{thmtools,thm-restate}
\usepackage{changepage}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{multirow,bigdelim}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{letltxmacro}
\usepackage{sansmath}
\usepackage{url}
\usepackage{flushend}
\usepackage{microtype}
\usepackage[utf8]{inputenc}
\usepackage{mathpartir}
\usepackage{empheq}
\usepackage{array}
\usepackage{pgfplots}
\usepackage{stmaryrd}
\usepackage{courier}
\usepackage{qtree}
\usepackage[normalem]{ulem}
\usepackage{relsize}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{tabularx}
\usepackage{stackengine}
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{remreset}
\usepackage{tabulary}
\usepackage{xspace}
\usepackage{bbm}
\usepackage{fullpage}
\usepackage[explicit]{titlesec}

% \renewcommand*\thesection{\arabic{section}.0}
% \renewcommand*\thesubsection{\arabic{section}.\arabic{subsection}}

@@

\section{SUMMARY}

\section{INTRODUCTION}

@@

We have written three academic papers~\cite{?}
describing and evaluating our algorithms and produced open-source our code that
implements those algorithms.

\section{METHODS, ASSUMPTIONS, AND PROCEDURES}

Our approach combines two strategies.  We use \textit{domain-specific programming
  language}, specifically, the Boomerang~\cite{boomerang, Matching10} language,
which is designed for writing bidirectional string transformations.  We also exploit
\textit{type- and example-directed program synthesis}, which uses enumerative
techniques to search a space of candidate solutions.  The search is constrained
by the type information about the program, as well as by example instances
provided by the user.

\subsection{Lenses and lens domain-specific programming languages}

A lens comprises two functions,
\emph{get} and \emph{put}.  The \emph{get} function translates
source data into the target format.  If the target data is updated, the
\emph{put} function translates this edited data back into the
source format.  
A benefit of lens-based languages is that they use a single term
to express both 
\emph{get} and \emph{put}.
Furthermore, well-typed lenses give rise to 
\emph{get} and \emph{put} functions 
guaranteed to satisfy desirable invertibility properties.

Lens-based languages are present in variety of tools and have found mainstream
industrial use.
Boomerang~\cite{boomerang, Matching10} lenses provide
guarantees on transformations between {\em ad hoc} string document formats.
Augeas~\cite{augeas}, a popular tool that reads Linux system configuration
files, uses the \emph{get} part of a lens to transform configuration
files into a canonical tree representation that users can edit
either manually or 
programmatically.  It uses the lens's \emph{put} to merge the edited
results back into the original string format.  Other lens-based languages and
tools include 
%
GRoundTram~\cite{Hidaka2011GRoundTramAI},
%
BiFluX~\cite{DBLP:conf/ppdp/PachecoZH14}, 
%
BiYacc~\cite{DBLP:conf/staf/ZhuK0SH15},
%
Brul~\cite{DBLP:conf/etaps/ZanLKH16},
%
BiGUL \cite{DBLP:conf/pepm/KoZH16}, 
%
bidirectional variants of 
relational algebra~\cite{BohannonPierceVaughan},
spreadsheet formulas~\cite{DBLP:conf/vl/MacedoPSC14},
graph query languages~\cite{DBLP:conf/icfp/HidakaHIKMN10},
and
XML transformation languages~\cite{DBLP:conf/pepm/LiuHT07}.

\subsection{Bijective lens synthesis}

As inputs, our bijective synthesis procedure takes regular expressions specifying the
source, $S$, and
target, $T$, formats, plus a collection of concrete examples of the desired 
transformation.  Format specifications are supplied as ordinary regular
expressions.
Because regular expressions are so widely understood, we anticipate such
inputs will be substantially easier for everyday programmers to work with
than the unfamiliar syntax of lenses.
Moreover, these format descriptions communicate a
great deal of information to the synthesis system.  Thus, requiring user input
of regular expressions makes synthesis robust, 
helps the system scale to large and complex data sources, and 
constrains the search space sufficiently that the user typically needs
to give very few, if any, examples.

The goal of the synthesis algorithm is to find a lens
$\ell : S \Leftrightarrow T$ that corresponds to a bijection from the language
of a source regular expression $S$ to a target language of a target regular
expression $T$.   Such a lens should satisfy the \textit{bijective lens laws}:

\begin{equation}\label{bijectivelenslaws} \ell.\get \;
  (\ell.\lput \; t) = t \text{, and } \ell.\lput \; (\ell.\get \; s) = s
\end{equation}

\begin{figure}
  \centering
  \small 
  \begin{tikzpicture}[auto,node distance=1.5cm]
    \node[text width=1.5cm,minimum height=.6cm,align=center,draw,rectangle] (todnfregex) {\ToDNFRegex{}};

    \node[align=right, anchor=east] (regex1) [left = .6cm of todnfregex.north west]{\Regex{}};
    \node[align=right, anchor=east] (regex2) [left = .6cm of todnfregex.south west]{\RegexAlt{}};
    \node[align=right, anchor=east] (exs) [below = .2cm of regex2]{ \Examples{} };

    \node[align=center] (dnfregex1) [right = .4cm of todnfregex.north east]{\DNFRegex{}};
    \node[align=center] (dnfregex2) [right = .4cm of todnfregex.south east]{\DNFRegexAlt{}};

    \node[text width=2.3cm,minimum height=.6cm,align=center,draw,rectangle] [right = 1.45cm of todnfregex.east] (synthdnflens) {\SynthDNFLens{}};
    \node[align=center] [above = .7cm of synthdnflens] (optician) {\Optician{}};

    \node[align=center] [right = .4cm of synthdnflens] (dnflens) {\DNFLens{}};

    \node[text width=1.5cm,minimum height=.6cm,align=center,draw,rectangle] [right = .4cm of dnflens] (tolens) {\ToLens{}};

    \node[align=center] [right = .6cm of tolens] (lens) {\Lens{}};

    \path[->] (regex1.east) edge (todnfregex.north west);
    \path[->] (regex2.east) edge (todnfregex.south west);

    \path[->] (todnfregex.north east) edge (dnfregex1.west);
    \path[->] (todnfregex.south east) edge (dnfregex2.west);

    \path[->] (dnfregex1.east) edge (synthdnflens.north west);
    \path[->] (dnfregex2.east) edge (synthdnflens.south west);

    \path[->] (synthdnflens) edge (dnflens);

    \path[->] (dnflens) edge (tolens);

    \path[->] (tolens) edge (lens);
    \draw[->] ($(exs.east)+(-3pt,0)$) -| node(exsedge) {} (synthdnflens);
    \node[fit={($(todnfregex.west)+(-4pt,0)$) ($(tolens.east)+(4pt,0)$) (exsedge) (dnfregex1) (optician) (dnfregex2)},draw] (surrounding) {};
    % Now place a relation (ID=rel1)
    %\node[text width=2cm,align=center,draw, rectangle] (sketch-gen) [right = .75cm of spec] {\TypeProp{}};
    %\node (below-gen) [below=.5cm of sketch-gen] {};
    %\node[text width=2cm,align=center,draw, rectangle] (sketch-compl)
    %     [right = .25cm of sketch-gen] {\RigidSynth{}};
    %\node (below-compl) [below=.5cm of sketch-compl] {};
    %\node[align=center] (lens) [right = .75cm of sketch-compl] {Lens}; 
    %% Draw an edge between rel1 and node1; rel1 and node2
    %\path[->] (spec) edge node (start-alg) {} (sketch-gen);
    %\path[->] (sketch-gen) edge node(middle) {} (sketch-compl);
    %\path[->] (sketch-compl) edge node[near start](success) {\Success{}} (lens);
    %\draw[<-] (sketch-gen.south) -- +(0,-.5) -| node[above left](failure){\Failure{}} (sketch-compl.south);

    %\node (synth-name) [above=.5cm of middle] {\Optician{}};
    %
    %\node[fit=(sketch-gen) (sketch-compl) (start-alg) (synth-name) (failure)
    %(success) ,draw] (surrounding) {};

  \end{tikzpicture}
  \caption{Schematic Diagram for \Optician{}.  Regular expressions, \Regex{} and
    \RegexAlt{}, and examples, \Examples{}, are given as input.
    First, the function \ToDNFRegex{} converts \Regex{} and \RegexAlt{} into
    their respective DNF forms, \DNFRegex{} and \DNFRegexAlt{}.
    Next, \SynthDNFLens{} synthesizes a DNF lens, \DNFLens{}, from \Regex{},
    \RegexAlt{}, and \Examples{}.
    Finally, \ToLens{} converts \DNFLens{} into \Lens{}, a lens in Boomerang
    that is equivalent to \DNFLens{}.}
  \label{fig:schematic-diagram-synthesis}
\end{figure}

Figure~\Cref{fig:schematic-diagram-synthesis} shows a high-level,
schematic diagram for \Optician{}.
First, \Optician{} uses the function \ToDNFRegex{} to convert the input
regular expressions into DNF regular expressions.  Next,
\SynthDNFLens{} performs type-directed synthesis on these DNF regular
expressions and the input examples to synthesize a DNF lens.  Finally, this DNF lens is
converted back into a regular lens with the function \ToLens{}, and returned to the user.

\subsection{Quotient lens synthesis}

Quotient lenses are lenses in which the lens laws are
loosened so that they hold modulo an equivalence relation on the source and
target data respectively; as above, we are concerned with {\em bijective
quotient lenses} which are lenses for which Equation \ref{bijectivelenslaws}
holds modulo equivalence relations $\equiv_S$ and $\equiv_T$ defined on the source
and target data respectively:

\begin{equation}\label{quotientlenslaws}
\ell.\get \; (\ell.\lput \; t) \equiv_T t \text{, and } \ell.\lput \; (\ell.\get
\; s) \equiv_S s
\end{equation}

The inputs to the quotient lens synthesis problem, as in the bijective case,
include source and target regular expressions $S$ and $T$ and a set of example
instances.  The equivalence relations $\equiv_S$ and $\equiv_T$ are also given
as inputs to the synthesis algorithm.  As we describe below, one result of our
work is a language of \textit{quotient regular expressions} that concisely
specifies $S$ and $\equiv_S$ simultaneously.

\section{RESULTS AND DISCUSSION}

@@

\section{CONCLUSIONS}
